Draft_Application_Stochastic_Volatility

### 2021-07-19 Real Dataset SV.Rmd
Aggiunto qualche grafico

@@

@@

@@

>>>>

```{r echo=FALSE, fig.align='center', fig.cap="Close to close percentage log returns, 3 indices", fig.height=4, fig.pos='H', fig.width=8, message=FALSE, warning=FALSE, results=F}
library(openxlsx)
library(ggplot2)
library(ggpubr)
data_SP500 <- read.xlsx("Dataset 17-21.xlsx", sheet = "SP500")
data_STOXX50E <- read.xlsx("Dataset 17-21.xlsx", sheet = "STOXX50E")
data_DJI <- read.xlsx("Dataset 17-21.xlsx", sheet = "DJI")

# DOW JONES

timestamp_DJI <- as.POSIXlt(data_DJI$Date, tz = "GMT", "%Y-%m-%d")
data_DJI<-cbind(data_DJI, timestamp=timestamp_DJI)

plot_DJI <- ggplot(data_DJI, aes(x=timestamp,y=log_close_to_close_return))+
  geom_line()+
  labs(x="Date",y="DJI")+
  theme_bw()

DJI_mean <- mean(data_DJI$log_close_to_close_return)
DJI_sd <- sd(data_DJI$log_close_to_close_return)

# S&P500

timestamp_SP <- as.POSIXlt(data_SP500$Date, tz = "GMT", "%Y-%m-%d")
data_SP500<-cbind(data_SP500, timestamp=timestamp_SP)

plot_SP <- ggplot(data_SP500, aes(x=timestamp,y=log_close_to_close_return))+
  geom_line()+
  labs(x="Date",y="S&P500")+
  theme_bw()

SP_mean <- mean(data_SP500$log_close_to_close_return)
SP_sd <- sd(data_SP500$log_close_to_close_return)

# STOXX50E

timestamp_STOXX <- as.POSIXlt(data_STOXX50E$Date, tz = "GMT", "%Y-%m-%d")
data_STOXX50E<-cbind(data_STOXX50E, timestamp=timestamp_STOXX)

plot_STOXX <- ggplot(data_STOXX50E, aes(x=timestamp,y=log_close_to_close_return))+
  geom_line()+
  labs(x="Date",y="STOXX50E")+
  theme_bw()

STOXX_mean <- mean(data_STOXX50E$log_close_to_close_return)
STOXX_sd <- sd(data_STOXX50E$log_close_to_close_return)

ggarrange(plot_DJI, plot_SP, plot_STOXX, nrow = 3, ncol = 1)

SC<-matrix(nrow=2,ncol=3)
rownames(SC)<-c("Mean","Standard Deviation")
colnames(SC) <- c("Dow Jones", "S&P500", "STOXX50E")

SC[1,1] = SP_mean
SC[1,2] = DJI_mean
SC[1,3] = STOXX_mean
SC[2,1] = SP_sd
SC[2,2] = DJI_sd
SC[2,3] = STOXX_sd

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library(kableExtra)
kbl(SC, align="c", longtable = T, booktabs = T, caption="Summary statistics, close to close percentage log returns",digits=5)
```

@@

```{r echo=FALSE, fig.align='center', fig.cap="Close to close percentage log returns, 3 indices", fig.height=4, fig.pos='H', fig.width=8, message=FALSE, warning=FALSE, results=F}

# Realized Volatility Plots

plotvolsp500<-ggplot(data_SP500, aes(x= timestamp, y=rv5))+
  geom_line()+
  labs(x="Date",y="SP")+
  theme_bw()

plotvoldji<-ggplot(data_DJI, aes(x= timestamp, y=rv5))+
  geom_line()+
  labs(x="Date",y="DJI")+
  theme_bw()

plotvolstoxx<-ggplot(data_STOXX50E, aes(x= timestamp, y=rv5))+
  geom_line()+
  labs(x="Date",y="STOXX")+
  theme_bw()
ggarrange(plotvolsp500,plotvoldji,plotvolstoxx,nrow = 3, ncol = 1)

@@

\section{Realised volatility as benchmark}

...
